\vskip.15in
\noindent\textbf{Deadline Policy}
Feel free to turn in assignments early.
Late assignments have a 10\% penalty if they are less than 1 day late, a 50\% penalty on the second day, and are not accepted later. 
We have this penalty so you can move on from past assignments and keep up with the current ones.
If an emergency arises, take care of yourself or whoever needs you first, then send a message to course staff when you are able.
Remember, even a poor grade is numerically more advantageous than a zero so always submit whatever you have!

\vskip.15in
\noindent\textbf{Attendance Expectation}
Lectures will include learning activities as well as information you will be responsible for at exam time to demonstrate your knowledge of reverse engineering.
Participation will be recorded during each lecture. 
It is anticipated that all good-faith efforts to participate will earn full credit. 
You have the freedom to miss up to 2 classes without penalty. 
Any further absences will require documentation.

\vskip.15in
\noindent\textbf{Collaboration}
Working together to understand how the malware samples work is encouraged. 
However, everyone must submit their own reports which include instructions on how another analyst could reproduce your results.
In exams, be prepared to individually demonstrate that you have learned to use the tools from the assignments.

\vskip.15in
\noindent\textbf{Etiquette}
Communications in class, with instructors, and online are expected to be professional and polite.

\vskip.15in
\noindent\textbf{Additional Information and University Policies}
Please visit https://provost.nmsu.edu/faculty-and-staff-resources/syllabus/policies for university policies and student services, including Discrimination and Disability Accommodation, academic misconduct, student services, final exam schedule, grading policies and more.  
