\vskip.15in
\noindent\textbf{Course Workload:}
\vskip.15in
Each week, the previous week's assignment will be due on Monday.
By Tuesday's class you will have read that week's textbook chapter (~20 pages).
You will be required to attend class and participate on Tuesdays and Thursdays.

In class, we will send the first \~20 minutes on lecture and questions.
The remainder of the class will be a lab section where everyone will work on the week's assignment.
Often, the instructor will prepare a demo or walk through the first steps of the project.
Everyone will be responsible for producing their own lab write-up each week.
But, working together and learning together is encouraged.
You will be responsible to be able to perform the lab techniques yourself on the exams.

You will submit all of your lab write-ups in GitHub, and you will be allowed to have these public to show to potential recruiters your skills.
The format of the reports will be markdown.
The reports will describe what you discovered about the malware we analyze, and how other analysts could reproduce and confirm your findings.

\newpage
\noindent \textbf{Course Outline:} 
\vspace*{.25in}

\begin{center} 
\begin{tabular}{|l|l|l|}
\textbf{Module} & \textbf{Description}                              & \textbf{Class Dates} \\
\hline
Module  0: & Ethics and Reverse Engineering Careers                 & 1/18 \\
Module  1: & Operational Security and Isolation                     & 1/23, 1/25 \\
Module  2: & Assembly, Program Memory Layout, Calling Conventions   & 1/30, 2/1  \\
Module  3: & Basic Static Analysis                                  & 2/6,  2/8  \\
Module  4: & Disassembly and Decompilation in IDA and Ghidra        & 2/13, 2/15 \\
Module  5: & Beginner Crackmes                                      & 2/20, 2/22 \\
Module  6: & Defeating Ransomware                                   & 2/27, 2/29  \\
Midterm Week & Review Tuesday, Exam Thursday 3/7 during class time  & 3/5,  \textbf{3/7}\\
--         & Spring Break                                           &  \\
Module  7: & Advanced Crackmes                                      & 3/19, 3/21 \\
Module  8: & Process Injection and Malware Static Analysis          & 3/26, 3/28 \\
Module  9: & Dynamic Analysis                                       & 4/2,  4/4  \\
Module 10: & Malware Behavior                                       & 4/9, 4/11 \\
Module 11: & Crypters and Packers                               & 4/16, 4/18 \\
Module 12: & Control Flow Integrity Attacks and Defenses            & 4/23, 4/25 \\
Module 13: & 64-bit Control Flow Hijacking                          & 4/30,  5/2  \\
Final Exam & Thursday 1-3PM in classroom                            & \textbf{5/9} \\
\end{tabular}
\end{center}


\vskip.25in
\noindent\textbf{Important Dates}:
\begin{center} \begin{minipage}{5in}
\begin{flushleft}
Drop Deadline \dotfill February 3\\
Withdraw Deadline \dotfill March 21\\
% Spring Break March 13-17
Midterm Exam Practicum \dotfill March 7\\
Final Exam Practicum \dotfill May 9\\
% Finals Week May 8-12
\end{flushleft}
\end{minipage}
\end{center}
